### 2014-06-27 alex/albania.Rmd
glory to albania

```{r possessions, echo=FALSE}
qplot()
```

>>>>

```{r possessions, echo=FALSE}
library(reshape2)
df = melt(student2012.sub %>% group_by(CNT, numposs, OECD) %>% summarise(mmath = mean(math), msci = mean(sci), mread = mean(read)), id=c("CNT", "numposs", "OECD"))
df$group = paste0(df$CNT, df$variable)
qplot(x = numposs, y = value, data = df, facets = ~OECD, geom = "line", color = variable, group = group)

qplot(x = numposs, y = mmath, data = student2012.sub %>% group_by(CNT, numposs, OECD) %>% summarise(mmath = mean(math), msci = mean(sci), mread = mean(read)), facets =~OECD, geom = "line", group = CNT) + ylab("Math Scores") 
```

```{r gender, echo=FALSE}

```
